An Efficient Calculus for Generalised Parikh Images of Regular Languages

### 2022-06-20 main.tex
Preliminary graphs

\usepackage{amsthm}
\usepackage{amsmath,mathtools,empheq,fancybox}
\usepackage{paralist}
\usepackage{url}
\usepackage{color}
\usepackage{textcomp,listings}
\usepackage{array}
\usepackage{mymacros}
\usepackage{microtype}
\usepackage{listings}
\usepackage{csquotes}
\usepackage{proof}
\usepackage{algorithm2e}

\usepackage{mathpartir}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

@@

@@

We evaluate the performance of \Catra{} on~\NrBenchmarks{} instances generated by the \Ostrich{} string constraint solver when solving the \Fudge{pyex benchmarks}. \Fudge{The instances are all enormous and have some on average 900 products of 400000 automata with 97 counters each and 9999 constraints}. After generating an initial~\InitialNrBenchmarks{}, we remove~\NrBroken{} misgenerated instances that did not parse, as well as~\NrTrivial{} instances solved in under five seconds by the baseline backend.

@@

In Figures~\ref{fig:solve-nr} and~\ref{fig:solve-division} we show how many of the~\NrBenchmarks{} the respective back-ends could solve and with which status. A full summary of their outcomes is also available in Table~\ref{tab:solve-status}. We see here \Fudge{that some solver is better than the others}.

\begin{figure}
  \caption{The number of solved instances per backend.}
  \label{fig:solve-nr}
\end{figure}

\begin{figure}
  \caption{The division of statuses per backend.}
  \label{fig:solve-division}
\end{figure}

@@

\begin{figure}
  \caption{The number of instances solved within a given number of seconds per backend.}
  \label{fig:cactus}
\end{figure}

@@

\begin{figure}
  \caption{The number of instances solved within a given number of seconds per backend.}
  \label{fig:cactus:image}
\end{figure}

>>>>

\usepackage{amsthm}
\usepackage{amsmath,mathtools,empheq,fancybox}
\usepackage{paralist}
\usepackage{url}
\usepackage{color}
\usepackage{textcomp,listings}
\usepackage{array}
\usepackage{mymacros}
\usepackage{microtype}
\usepackage{listings}
\usepackage{csquotes}
\usepackage{proof}
\usepackage{algorithm2e}      
\usepackage{multirow}
\usepackage{mathpartir}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

@@

\contents{
  \item introducera homomorfismen
  \item start with length
  \item räkna bara a och b, strunta i c
  \item ändra till >= för att illustrera splitting
  }

@@

We evaluate the performance of \Catra{} on~\NrBenchmarks{} instances generated by the \Ostrich{} string constraint solver when solving the \Fudge{pyex benchmarks}. \Fudge{The instances are all enormous and have some on average 900 products of 400000 automata with 97 counters each and 9999 constraints}. After generating an initial~\InitialNrBenchmarks{}, we remove~\NrBroken{} misgenerated instances that did not parse, as well as~\NrTrivial{} instances solved in under five seconds by the baseline backend. The benchmarks are run on commit \texttt{\commit}.

@@

In Figures~\ref{fig:solve-division} we show how many of the~\NrBenchmarks{} the respective back-ends could solve and with which status. A full summary of their outcomes is also available in Table~\ref{tab:solve-status}. We see here \Fudge{that some solver is better than the others}.

\begin{table}[ht]
  \centering
  \input{graphs/solved_pivot_table.tex}
  \caption{The result of running the respective back-ends by instance
  satisifiability (satisifiable or unsatisifiable) with a timeout of
  \RuntimeTimeout. Instances solved by no backend within the timeout are omitted
  from the table. }\label{tab:solve-status}
\end{table}

\begin{figure}
  \includegraphics[width=0.75\linewidth]{graphs/\commit-by-solver.pdf}
  \caption{The division of statuses per backend.}
  \label{fig:solve-division}
\end{figure}

\begin{figure}
  \includegraphics[width=0.75\linewidth]{graphs/\commit-time-boxplot.pdf}
  \caption{The distribution of runtimes for solved instances per backend. Note that the number of instances solved differs between backends.}
  \label{fig:runtime-boxplot}
\end{figure}

\begin{figure}
  \includegraphics[width=0.75\linewidth]{graphs/\commit-duels-scatter.pdf}
  \caption{The pairwise runtime of each instance for instances solved by any backend. Timeouts are reported as a runtime of \RuntimeTimeout.}
  \label{fig:duels}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.75\linewidth]{graphs/\commit-cactus.pdf}
  \caption{The number of instances solved as the time budget increases, simulated from one \RuntimeTimeout-timeout run.}
  \label{fig:cactus}
\end{figure}

@@

\begin{figure}
  \caption{The number of instances \Catra{} was able to find the Presburger form of the image for within a given number of seconds per backend.}
  \label{fig:cactus:image}
\end{figure}
